Pre-/Post-Trikafta in CFRD

### 2024-05-06 Colleen Wood/Pre-post Trikafta/pre_post_trikafta_analysis.Rmd
base plots for colleen done

```{r}
df %>%
  select(
    `CFF ID`, `Pre or Post`, `Num. A1c Values`, HbA1c, Time, Weight,
    `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  tbl_summary(
    by = `Pre or Post`, type = list(
      c(
        "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
        "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
      ) ~ "continuous2"
    ),
    statistic = list(
      c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
        c("{mean} ± {sd}", "{min}, {max}"),
      c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
        c("{median} [{p25}, {p75}]", "{min}, {max}")
    ),
    include = -`CFF ID`, digits = list(everything() ~ 2),
    missing_text = "Missing"
  ) %>%
  add_p(
    test = list(
      c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile", "TDD") ~
        "paired.wilcox.test",
      c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
    ),
    group = `CFF ID`
  ) %>%
  separate_p_footnotes()
```

@@

```{r}
df %>%
  select(
    `CFF ID`, `Pre or Post`, Site, `Num. A1c Values`, HbA1c, Time,
    Weight, `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  tbl_strata(
    strata = Site,
    .tbl_fun = ~ .x %>%
      tbl_summary(
        by = `Pre or Post`, type = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
          ) ~ "continuous2"
        ),
        statistic = list(
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
            c("{mean} ± {sd}", "{min}, {max}"),
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
            c("{median} [{p25}, {p75}]", "{min}, {max}")
        ),
        include = -`CFF ID`, digits = list(everything() ~ 2),
        missing_text = "Missing"
      ) %>%
      add_p(
        test = list(
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile", "TDD") ~
            "paired.wilcox.test",
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
        ),
        group = `CFF ID`
      ) %>%
      separate_p_footnotes()
  )
```

@@

```{r}
df %>%
  select(
    `CFF ID`, `Pre or Post`, `Baseline HbA1c`, `Num. A1c Values`, HbA1c, Time,
    Weight, `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  tbl_strata(
    strata = `Baseline HbA1c`,
    .tbl_fun = ~ .x %>%
      tbl_summary(
        by = `Pre or Post`, type = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
          ) ~ "continuous2"
        ),
        statistic = list(
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
            c("{mean} ± {sd}", "{min}, {max}"),
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
            c("{median} [{p25}, {p75}]", "{min}, {max}")
        ),
        include = -`CFF ID`, digits = list(everything() ~ 2),
        missing_text = "Missing"
      ) %>%
      add_p(
        test = list(
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile", "TDD") ~
            "paired.wilcox.test",
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
        ),
        group = `CFF ID`
      ) %>%
      separate_p_footnotes()
  )
```

@@

```{r}
df %>%
  select(
    `CFF ID`, `Pre or Post`, `Baseline BMI`, `Num. A1c Values`, HbA1c, Time,
    Weight, `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  tbl_strata(
    strata = `Baseline BMI`,
    .tbl_fun = ~ .x %>%
      tbl_summary(
        by = `Pre or Post`, type = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
          ) ~ "continuous2"
        ),
        statistic = list(
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
            c("{mean} ± {sd}", "{min}, {max}"),
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
            c("{median} [{p25}, {p75}]", "{min}, {max}")
        ),
        include = -`CFF ID`, digits = list(everything() ~ 2),
        missing_text = "Missing"
      ) %>%
      add_p(
        test = list(
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile", "TDD") ~
            "paired.wilcox.test",
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
        ),
        group = `CFF ID`
      ) %>%
      separate_p_footnotes()
  )
```

@@

```{r}
df %>%
  select(
    `CFF ID`, `Pre or Post`, `Post BMI`, `Num. A1c Values`, HbA1c, Time,
    Weight, `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  filter(!is.na(`Post BMI`)) %>%
  tbl_strata(
    strata = `Post BMI`,
    .tbl_fun = ~ .x %>%
      tbl_summary(
        by = `Pre or Post`,
        type = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
          ) ~ "continuous2"
        ),
        statistic = list(
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
            c("{mean} ± {sd}", "{min}, {max}"),
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
            c("{median} [{p25}, {p75}]", "{min}, {max}")
        ),
        include = -`CFF ID`, digits = list(everything() ~ 2),
        missing_text = "Missing"
      ) %>%
      add_p(
        test = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "TDD"
          ) ~ "paired.wilcox.test",
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
        ),
        group = `CFF ID`
      ) %>%
      separate_p_footnotes()
  )
```

>>>>

```{r}
# Table
df %>%
  select(
    `CFF ID`, `Pre or Post`, `Num. A1c Values`, HbA1c, Time, Weight,
    `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  tbl_summary(
    by = `Pre or Post`, type = list(
      c(
        "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
        "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
      ) ~ "continuous2"
    ),
    statistic = list(
      c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
        c("{mean} ± {sd}", "{min}, {max}"),
      c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
        c("{median} [{p25}, {p75}]", "{min}, {max}")
    ),
    include = -`CFF ID`, digits = list(everything() ~ 2),
    missing_text = "Missing"
  ) %>%
  add_p(
    test = list(
      c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile", "TDD") ~
        "paired.wilcox.test",
      c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
    ),
    group = `CFF ID`
  ) %>%
  separate_p_footnotes()
# Plot
ggplot(df, aes(x = `Pre or Post`, y = HbA1c, group = `CFF ID`)) +
  geom_point(alpha = 0.2) +
  geom_line(alpha = 0.2) +
  theme_classic() +
  theme(axis.title.x = element_blank())
```

@@

```{r}
# Table
df %>%
  select(
    `CFF ID`, `Pre or Post`, Site, `Num. A1c Values`, HbA1c, Time,
    Weight, `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  tbl_strata(
    strata = Site,
    .tbl_fun = ~ .x %>%
      tbl_summary(
        by = `Pre or Post`,
        type = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
          ) ~ "continuous2"
        ),
        statistic = list(
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
            c("{mean} ± {sd}", "{min}, {max}"),
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
            c("{median} [{p25}, {p75}]", "{min}, {max}")
        ),
        include = -`CFF ID`, digits = list(everything() ~ 2),
        missing_text = "Missing"
      ) %>%
      add_p(
        test = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "TDD"
          ) ~ "paired.wilcox.test",
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
        ),
        group = `CFF ID`
      ) %>%
      separate_p_footnotes()
  )
# Plot
ggplot(df, aes(x = `Pre or Post`, y = HbA1c, group = `CFF ID`)) +
  geom_point(alpha = 0.2) +
  geom_line(alpha = 0.2) +
  theme_classic() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(~Site)
```

@@

```{r}
# Table
df %>%
  select(
    `CFF ID`, `Pre or Post`, `Baseline HbA1c`, `Num. A1c Values`, HbA1c, Time,
    Weight, `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  tbl_strata(
    strata = `Baseline HbA1c`,
    .tbl_fun = ~ .x %>%
      tbl_summary(
        by = `Pre or Post`,
        type = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
          ) ~ "continuous2"
        ),
        statistic = list(
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
            c("{mean} ± {sd}", "{min}, {max}"),
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
            c("{median} [{p25}, {p75}]", "{min}, {max}")
        ),
        include = -`CFF ID`, digits = list(everything() ~ 2),
        missing_text = "Missing"
      ) %>%
      add_p(
        test = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "TDD"
          ) ~ "paired.wilcox.test",
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
        ),
        group = `CFF ID`
      ) %>%
      separate_p_footnotes()
  )
# Plot
ggplot(df, aes(x = `Pre or Post`, y = HbA1c, group = `CFF ID`)) +
  geom_point(alpha = 0.2) +
  geom_line(alpha = 0.2) +
  theme_classic() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(~`Baseline HbA1c`)
```

@@

```{r}
# Table
df %>%
  select(
    `CFF ID`, `Pre or Post`, `Baseline BMI`, `Num. A1c Values`, HbA1c, Time,
    Weight, `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  tbl_strata(
    strata = `Baseline BMI`,
    .tbl_fun = ~ .x %>%
      tbl_summary(
        by = `Pre or Post`,
        type = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
          ) ~ "continuous2"
        ),
        statistic = list(
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
            c("{mean} ± {sd}", "{min}, {max}"),
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
            c("{median} [{p25}, {p75}]", "{min}, {max}")
        ),
        include = -`CFF ID`, digits = list(everything() ~ 2),
        missing_text = "Missing"
      ) %>%
      add_p(
        test = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "TDD"
          ) ~ "paired.wilcox.test",
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
        ),
        group = `CFF ID`
      ) %>%
      separate_p_footnotes()
  )
# Plot
ggplot(df, aes(x = `Pre or Post`, y = HbA1c, group = `CFF ID`)) +
  geom_point(alpha = 0.2) +
  geom_line(alpha = 0.2) +
  theme_classic() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(~`Baseline BMI`)
```

@@

```{r}
# Table
df %>%
  select(
    `CFF ID`, `Pre or Post`, `Post BMI`, `Num. A1c Values`, HbA1c, Time,
    Weight, `BMI Percentile`, ppFEV1, ppFEV1gl, ppFVC, ppFVCgl, TDD,
  ) %>%
  filter(!is.na(`Post BMI`)) %>%
  tbl_strata(
    strata = `Post BMI`,
    .tbl_fun = ~ .x %>%
      tbl_summary(
        by = `Pre or Post`,
        type = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl", "TDD"
          ) ~ "continuous2"
        ),
        statistic = list(
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~
            c("{mean} ± {sd}", "{min}, {max}"),
          c("Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile") ~
            c("{median} [{p25}, {p75}]", "{min}, {max}")
        ),
        include = -`CFF ID`, digits = list(everything() ~ 2),
        missing_text = "Missing"
      ) %>%
      add_p(
        test = list(
          c(
            "Num. A1c Values", "HbA1c", "Time", "Weight", "BMI Percentile",
            "TDD"
          ) ~ "paired.wilcox.test",
          c("ppFEV1", "ppFEV1gl", "ppFVC", "ppFVCgl") ~ "paired.t.test"
        ),
        group = `CFF ID`
      ) %>%
      separate_p_footnotes()
  )
# Plot
ggplot(
  df[!is.na(df$`Post BMI`), ],
  aes(x = `Pre or Post`, y = HbA1c, group = `CFF ID`)
) +
  geom_point(alpha = 0.2) +
  geom_line(alpha = 0.2) +
  theme_classic() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(~`Post BMI`)
```
